A performance comparison of Dask and Apache Spark for data-intensive neuroimaging pipelines

### 2019-07-29 latex/paper.tex

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/spark_histo_gantt.png}
        \caption{Spark}\label{fig:histo_spark_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/bag_histo_gantt.png}%
        \caption{Dask Bag}\label{fig:histo_dask_bag_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/delayed_histo_gantt.png}%
        \caption{Dask Delayed}\label{fig:histo_dask_delayed_gantt}
    \end{subfigure}
    \caption{Histogram (Python): 125 blocks, 8 workers, 8
    CPUs/worker}\label{fig:histo_gantt}
\end{figure}

>>>>

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \href{https://zenodo.org/record/3354434/files/spark-histo-baseline.html?download=1}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/spark_histo_gantt.png}}
        \caption{Spark}\label{fig:histo_spark_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://zenodo.org/record/3354434/files/dask-bag-histo-baseline.html?download=1}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/bag_histo_gantt.png}}
        \caption{Dask Bag}\label{fig:histo_dask_bag_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://zenodo.org/record/3354434/files/dask-delayed-histo-baseline.html?download=1}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/delayed_histo_gantt.png}}
        \caption{Dask Delayed}\label{fig:histo_dask_delayed_gantt}
    \end{subfigure}
    \caption{Histogram (Python): 125 blocks, 8 workers, 8
    CPUs/worker}\label{fig:histo_gantt}
\end{figure}
